Information for DOE Report

### 2015-11-28 DOESummaryNov2015/DOESummaryNov2015.tex
Added 2 figures.

\begin{figure}
  \centering
  \includegraphics[angle=270,origin=c,width=\textwidth]{figures/integratedADC.pdf}
  \caption{Integrated ADC for the four SiPM channels.}
  \label{fig:cddfadc}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[angle=270,origin=c,width=.7\textwidth]{figures/integratedADC.pdf}
  \caption{Integrated ADC for the four SiPM channels.}
  \label{fig:cddfadc}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[angle=270,origin=c,width=.7\textwidth]{figures/calibrated_spectra.pdf}
  \caption{ADC to photoelectron calibration for the four SiPM channels.}
  \label{fig:cddfcalibrated}
\end{figure}

Figure~\ref{fig:cddfcalibrated} shows calibrated photoelectron(PE) spectra for the four channels. The calibration was done by assigning the first peak to 1 PE, the second to 2 PE, etc.
